\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}
\hyphenpenalty=750

% Remove page numbers (optional)
%\pagenumbering{gobble}

\begin{document}

%-------------------- HEADER --------------------%
    \begin{center}
    {\Large \textbf{KIRAN SURESH SARODE}}\\[3pt]
    \normalsize
    \href{mailto:ksarode.pro@gmail.com}{ksarode.pro@gmail.com}  | +91 95453 81830 | Immediate Joiner
    \href{https://www.linkedin.com/in/kiransarode}{linkedin.com/in/kiransarode} | 
    \href{https://github.com/ksarode-pro}{github.com/ksarode-pro}  | 
    Vasai, Palghar, MH, India
\end{center}
%-------------------- SUMMARY --------------------%
\section*{Professional Summary}
Over 11 years of hands-on experience in end-to-end software development, focusing on \textbf{Fintech}, \textbf{Digital Payments}, \textbf{Loyalty and Employee Rewards} domains. Demonstrated expertise in designing and delivering secure and scalable solutions. Additionally, contributed technically to business operations in \textbf{Merchant and Client Onboarding}. Proven track record in leading cross-functional teams using the \textbf{Scrum framework (Agile methodology)}, ensuring high-quality and timely delivery. Adept at collaborating with global stakeholders, integrating external APIs/services, and optimizing performance while enhancing security for high-availability systems.

%-------------------- CORE COMPETENCIES --------------------%
\section*{Core Competencies}
\begin{itemize}
    \item \textbf{Languages:} C\#, T-SQL
    \item \textbf{Frameworks:} .NET Core 6+, .NET Framework 4.8, Angular 13+, MVC
    \item \textbf{Microservices Architecture:} ASP.NET WebAPIs, gRPC,  GraphQL, Message Queuing
    \item \textbf{Database Management:} Azure SQL, MS SQL Server, EF Core
    \item \textbf{Development Tools \& IDEs:} Visual Studio 2022, VS Code, GitHub Copilot, Cursor AI, Postman
    \item \textbf{Version Control:} Azure Repos, Git
    \item \textbf{Agile Leadership:} Scrum Framework, Sprint Planning, Scrum Ceremonies, Technical Team Management
    \item \textbf{Cloud \& DevOps:} Azure Repo, Azure PaaS Services such as Service Bus, Key Vault, Application Insights, Azure SQL, Azure Blob Storage, Basics of Docker and Kubernetes
    \item \textbf{Testing \& QA:} xUnit, MOQ, Postman, SoapUI, JMeter
    \item \textbf{Technical Documentation:} Confluence, Sequence and Component Diagrams, API Contract Documentation, Solution Design Documents (LLD)
\end{itemize}

%-------------------- ACHIEVEMENTS --------------------%
\section*{Achievements \& Awards}
\begin{itemize}
    \item \textbf{Star Employee Award} -- Recognized by Edenred APAC management (Singapore, Jan 2024).
    \item \textbf{Shortlisted and enrolled in the Leadership Development Program} -- Nominated by Edenred APAC HQ (Paris, Nov 2022).
    \item \textbf{Edenred Eagles Bronze \& XTRAMILE} (Q4 2019) -- Recognized with the most prestigious awards for significant technical contributions to digital voucher integrations and TX2 technical operations by Edenred India management.
    \item \textbf{7 Applause Awards} (Aug 2016--Oct 2021) -- For \textbf{TX2 platform launch}, \textbf{merchant onboarding}, \textbf{on-prem to Azure DB migration}, and critical \textbf{3rd-party voucher procurement integrations and automations} (Amazon, Croma, Joyalukkas, etc.).
\end{itemize}

%-------------------- PROFESSIONAL EXPERIENCE --------------------%
\section*{Professional Experience}

\textbf{Freelancing} \hfill \textit{Jan 2025 -- Present}\\
\textit{Fullstack Software Engineer}
\begin{itemize}
    \item \textbf{Led full software development lifecycle (SDLC)} — from requirement gathering and analysis to deployment and post-production support — ensuring \textbf{code quality}, \textbf{traceability}, and \textbf{stable releases}.
    \item \textbf{Architected and developed} a \textbf{monolithic application} using \textbf{Clean Architecture} and \textbf{CQRS (Command-Query Responsibility Segregation)} to achieve clear separation of concerns and maintainability.
    \item \textbf{Implemented} robust \textbf{ASP.NET Core Web APIs} with \textbf{Entity Framework Core (EF Core)} for entity modeling, migrations, command/query handlers, and domain services; used \textbf{SQL Server 2017} as the primary database.
    \item \textbf{Integrated} advanced \textbf{security features} including \textbf{JWT-based authentication}, \textbf{role/permission-based authorization}, \textbf{centralized exception handling}, and \textbf{API versioning} to ensure scalability and reliability.
    \item \textbf{Developed} the frontend using \textbf{Angular 19} and \textbf{Bootstrap 5}, implementing \textbf{modular routing}, \textbf{stateful components}, and \textbf{REST API integrations} for a responsive and consistent UI experience.
    \item \textbf{Collaborated} with stakeholders to \textbf{gather and refine requirements}, prepared \textbf{Business Requirement Documents (BRD)}, and authored detailed \textbf{user stories} with \textbf{acceptance criteria}.
    \item \textbf{Authored automated unit tests} using \textbf{xUnit}, developed \textbf{Moq-based test doubles}, and maintained \textbf{Postman} collections for \textbf{UAT and regression testing}.
    \item Utilized\textbf{ Git and GitHub} for version control, branching, and code reviews; configured \textbf{UAT and Production environments} on \textbf{Virtual Machines (VMs)} for smooth CI/CD and deployment.
    \item Utilized \textbf{Cursor AI} to accelerate code generation, improve boilerplate consistency, and enhance development productivity.
\end{itemize}
\newline
\textbf{Edenred, Singapore (Remote)} \hfill \textit{Jan 2022 -- Oct 2024}\\
\textit{Tech Lead (Jan 2023 -- Oct 2024)},
\newline
\textit{Senior Software Developer (Jan 2022 -- Dec 2022)}
\begin{itemize}
    \item \textbf{Led} a cross-functional India-based team (5 Developers, 2 QA, 1 Product Manager, 1 Scrum Master) to deliver the \textbf{Ticket XPress Cloud} platform using the \textbf{Agile Scrum} framework.
    \item \textbf{Designed and developed} event-driven \textbf{microservices} for transactions, client, distribution, and smart voucher modules using \textbf{.NET 6}, \textbf{ASP.NET Core Web APIs}, \textbf{gRPC}, \textbf{Azure Service Bus}, \textbf{Azure Functions}, \textbf{Azure SQL}, and \textbf{EF Core 6}; enhanced the \textbf{Audit (ADT)} microservice with \textbf{Cosmos DB} for scalable NoSQL audit logging.
    \item \textbf{Modernized} the \textbf{TX Smart Voucher} (MVC-based) application by migrating from legacy \textbf{TX2 APIs} to \textbf{TXC APIs}, improving system performance; implemented \textbf{Redis caching} for high-frequency data and \textbf{GraphQL} for optimized read/query operations.
    \item \textbf{Developed} key components for the \textbf{TOC (TXC Operations Center)} web app using \textbf{Angular} and integrated APIs with cloud services.
    \item \textbf{Migrated} legacy on-premises APIs to \textbf{cloud-native microservices} with \textbf{GraphQL} and \textbf{gRPC}, ensuring seamless integration with global business unit applications.
    \item \textbf{Integrated} all microservices with \textbf{Azure Application Insights} for advanced monitoring, performance metrics, and service-to-service tracing.
    \item \textbf{Collaborated} with the \textbf{DevOps} team to implement \textbf{CI/CD pipelines} using \textbf{Docker}, \textbf{Kubernetes (Azure AKS)}, and \textbf{Azure Pipelines}, improving deployment efficiency and scalability.
    \item \textbf{Partnered} with global business units (India, Taiwan, Global Rewards) for requirements gathering, and worked with \textbf{security/compliance} teams to ensure secure and compliant development.
    \item \textbf{Contributed} to architecture and technical documentation, assisting in \textbf{low-level design} and maintaining detailed \textbf{system documentation}.
    \item \textbf{Conducted} code reviews, \textbf{authored unit tests}, and optimized application performance for high-volume eVoucher transactions.
    \item \textbf{Managed} source code using \textbf{Azure Repos}, enforcing \textbf{branching strategy}, \textbf{code versioning}, and \textbf{best development practices}. 
    \item Utilized \textbf{GitHub Copilot} to enhance team's development productivity.
\end{itemize}

\textbf{Edenred, Thane, Maharashtra, India} \hfill \textit{May 2015 -- Dec 2021}\\
\textit{Project Lead (Jan 2020 -- Dec 2021), \newline Team Lead (Jan 2017 -- Dec 2019), \newline Software Developer (May 2015 -- Dec 2016)}
\begin{itemize}
    \item \textbf{Led} a cross-functional team of 4–5 members, implementing \textbf{Scrum ceremonies}, \textbf{backlog prioritization}, and \textbf{sprint planning} to ensure timely and high-quality delivery.
    \item \textbf{Provided technical leadership} in replacing the legacy \textbf{EMV (Email and Mobile Voucher)} system with the \textbf{Ticket XPress 2 (TX2)} platform — a scalable \textbf{digital eVoucher management solution} serving \textbf{300+ merchants} and \textbf{250+ enterprise clients} across India.
    \item \textbf{Designed and developed} the \textbf{TX2 Merchant} and \textbf{Admin Dashboard} applications to support merchants and Edenred’s backend team in managing customer queries and transactions.
    \item \textbf{Offered technical consultation} to external clients and merchant tech teams for \textbf{POS}, \textbf{e-commerce}, and \textbf{mobile app integrations} with TX2 via \textbf{POS} and \textbf{Biz APIs}, ensuring seamless integration and user experience.
    \item \textbf{Integrated third-party eVoucher procurement APIs} with major merchants (\textbf{Flipkart, Amazon India, Croma, Puma}), enabling \textbf{secure, automated payment} and \textbf{settlement workflows}.
    \item \textbf{Designed and developed} \textbf{EmployEase}, an \textbf{Employee Recognition Management Platform}, and successfully onboarded enterprise clients including \textbf{XL Catlin, Airtel, Omega Healthcare, and SBI Cards}.
    \item \textbf{Led the migration} of on-premises databases to \textbf{Azure SQL DB} with minimal downtime, improving scalability and availability.
\end{itemize}

\textbf{Freelance Work\hfill }\textit{Jun 2017 -- Aug 2017}\textbf{}
\begin{itemize}
    \item Developed \textbf{AMC Technology} website using ASP.NET 4.5 and Bootstrap.\textbf{\\}
\end{itemize}

\textbf{Zerebral IT Solutions, Vasai, Maharashtra} \hfill \textit{Jan 2013 -- May 2015}\\
\textit{Software Engineer (Jul 2013 -- May 2015), \newline Trainee (Jan 2013 -- May 2013)}
\begin{itemize}
    \item Developed and maintained \textbf{Hathway LCO Prepaid System}, enabling local cable operators (LCOs) to manage \textbf{service activations, channel plans, and billing} for India's largest MSO/broadband provider Hathway.
\end{itemize}

%-------------------- EDUCATION --------------------%
\section*{Education}
\begin{itemize}
    \item \textbf{MCA} -- Sardar Patel Institute of Technology,  University of Mumbai, 2013 \quad (64.78\%)
    \item \textbf{B.Sc. (IT)} -- VIVA College, University of Mumbai, 2010 \quad (65.55\%)
\end{itemize}
%-------------------- PERSONAL DETAILS --------------------%
\section*{Interests}
\begin{itemize}
    \item Drawing, painting, browsing the Internet, and listening to music
\end{itemize}
\vspace{16pt}


\end{document}
